\documentclass[conference]{IEEEtran}

\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{todonotes}
% \usepackage{amssym}
% \usepackage{amsthm}

\begin{document}

\title{An Exploration of Bitcoin Anonymity}


\author{\IEEEauthorblockN{Christopher A. Wood}
\IEEEauthorblockA{Department of Computer Science\\
University of California Irvine\\
Email: woodc1@uci.edu}
\and
\IEEEauthorblockN{Chris H. Vu}
\IEEEauthorblockA{Department of Computer Science\\
University of California Irvine\\
Email: ChrisHVu@gmail.com}}

% make the title area
\maketitle

\begin{abstract}
TODO
\end{abstract}

\IEEEpeerreviewmaketitle

\input{01-introduction}
\input{02-overview}
\input{03-security}
\input{04-attacks}
\input{05-problems}
\input{06-related}
\input{07-conclusion}

\begin{thebibliography}{1}

\bibitem{bitcoin} Satoshi Nakamoto. Bitcoin: A Peer-to-Peer Electronic Cash System. \emph{Consulted} 1 (2008).

\bibitem{Chaum81-Mix} David L. Chaum. Untraceable electronic mail, return addresses, and digital pseudonyms. \emph{Communications of the ACM} 24(2) (1981), 84-90.

\bibitem{chaumain} David L. Chaum. Blind Signatures for Untraceable Payments. \emph{Crypto} 82 (1982).

\bibitem{zerocoin} Ian Miers, Christina Garman, Matthew Green, Aviel D. Rubin. Zerocoin: Anonymous Distributed E-Cash from Bitcoin. \emph{IEEE Symposium on Security and Privacy} (2013).

\bibitem{Androulaki12-privacy} Elli Androulaki, Ghassan O. Karame, Marc Roeschlin, Tobias Scherer, and Srdjan Capkun. Evaluating User Privacy in Bitcoin. \emph{IACR Cryptology ePrint Archive} 596 (2012).

\bibitem{Shamir13-bitcoingraph} Dorit Ron and Adi Shamir. Quantitative Analysis of the Full Bitcoin Transaction Graph. \emph{IACR Cryptology ePrint Archive} 584 (2012).

\bibitem{ReidHarrigan13} Fergal Reid and Martin Harrigan. An Analysis of Anonymity in the Bitcoin System. \emph{Security and Privacy in Social Networks}, Springer New York (2013), 197-223.

\bibitem{BetterToBitter} Simon Barber, Xavier Boyen, Elaine Shi, and Ersin Uzun. Bitter to Better -- How to Make Bitcoin a Better Currency. \emph{Financial Cryptography and Data Security}, Springer Berlin Heidelberg (2012), 399-414.

\bibitem{Fistful12} Sarah Meiklejohn, Marjori Pomarole, Grant Jordan, Kirill Levchenko, Damon McCoyy, Geoffrey M. Voelker, and  Stefan Savage. A Fistful of Bitcoins: Characterizing Payments Among Men with No Names. In \emph{Proceedings of the 2013 Conference on Internet Measurement Conference}, ACM (2013).

\bibitem{kaminsky} Dan Kaminsky. Black Ops of TCP/IP Presentation. \emph{Black Hat, Chaos Communication
Camp} (2011).

\bibitem{bitcoin-tor-wiki} Tor. Bitcoin Wiki. Available online at \url{https://en.bitcoin.it/wiki/Tor}. Last accessed: 1/25/14.

\bibitem{coinjoin} G. Maxwell. Coinjoin: Bitcoin Privacy for the Real World. Available online at \url{https://bitcointalk.
org/index.php?topic=279249.0}. Last accessed: 1/31/14.

\bibitem{pinocchio} George Danezis, C\'{e}dric Fournet, Markulf Kohlweiss, Bryan Parno. Pinocchio Coin: Building Zerocoin from a Succinct Pairing-Based Proof System. In \emph{Proceedings of the First ACM Workshop on Language Support for Privacy-Enhancing Technologies}, ACM (2013).

\bibitem{mixcoin} Joseph Bonneau, Arvind Narayan, Andrew Miller, Jeremy Clark, and Joshua A. Kroll. Mixcoin - Anonymity for Bitcoin with accountable mixes. Preprint available online at: \url{http://cs.umd.edu/~amiller/mix.pdf}.

\bibitem{nist-beacon} NIST Randomness Beacon. Available online at: \url{http://www.nist.gov/itl/csd/ct/nist_beacon.cfm}. Last accessed: 2/5/14.

\bibitem{privacy-19} N. X. Vinh, J. Epps, and J. Bailey. Information Theoretic Measures for Clusterings Comparison: Is a Correction for Chance Necessary? In \emph{26th Annual International Conference on Machine Learning (ICML)} (2009).

\bibitem{privacy-20} N. X. Vinh, J. Epps, and J. Bailey. Information Theoretic Measures for Clusterings Comparison: Variants, Properties, Normalization and Correction for Chance. \emph{Journal of Machine Learning Research} (2010).

\bibitem{zkpdl} Sarah Meiklejohn, C. Chris Erway, Alptekin K\o{u}pc\o{u}, Theodora Hinkle, and Anna Lysyanskaya. ZKPDL: A Language-Based System for Efficient Zero-Knowledge Proofs and Electronic Cash. \emph{USENIX Security Symposium}, (10) (2010).

\bibitem{tor-attack1} Steven J. Murdoch and George Danezis. Low-Cost Traffic Analysis of Tor. \emph{IEEE Symposium on Security and Privacy} (2005).

\bibitem{tor-attack2} Brian N. Levine, Michael K. Reiter, Chenxi Wang, and Matthew Wright. Timing Attacks in Low-Latency Mix Systems. \emph{Financial Cryptography, Springer Berlin Heidelberg} (2004).

\end{thebibliography}




% that's all folks
\end{document}


