\documentclass[conference]{IEEEtran}

\usepackage{todonotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{colortbl}
% \usepackage[table]{xcolor}

\usepackage{listings}

\usepackage{color}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}

\lstset{
  basicstyle=\ttfamily\small,
  columns=fullflexible,
  showstringspaces=false,
  commentstyle=\color{gray}\upshape
}

\lstdefinelanguage{XML}
{
  morestring=[b]",
  morestring=[s]{>}{<},
  morecomment=[s]{<?}{?>},
  stringstyle=\color{black},
  identifierstyle=\color{darkblue},
  keywordstyle=\color{cyan},
  morekeywords={xmlns,version,type}% list your attributes here
}

\newcounter{eqn}
\renewcommand*{\theeqn}{\alph{eqn})}
\newcommand{\num}{\refstepcounter{eqn}\text{\theeqn}\;}

\makeatletter
\newcommand{\putindeepbox}[2][0.7\baselineskip]{{%
    \setbox0=\hbox{#2}%
    \setbox0=\vbox{\noindent\hsize=\wd0\unhbox0}
    \@tempdima=\dp0
    \advance\@tempdima by \ht0
    \advance\@tempdima by -#1\relax
    \dp0=\@tempdima
    \ht0=#1\relax
    \box0
}}
\makeatother

\begin{document}

\title{Bitcoin Boomerang \\ {\LARGE Collaborative Anonymity for Transaction Broadcasting}}

\author{\IEEEauthorblockN{Christopher A. Wood}
\IEEEauthorblockA{Department of Computer Science\\
University of California Irvine\\
Email: woodc1@uci.edu}
\and
\IEEEauthorblockN{Chris H. Vu}
\IEEEauthorblockA{Department of Computer Science\\
University of California Irvine\\
Email: ChrisHVu@gmail.com}}

% make the title area
\maketitle

\begin{abstract}
Sender anonymity is important in the design of several ``cryptographically-enhanced'' variations of Bitcoin, such as ZeroCoin \cite{zerocoin}. Consequently, they often state that users install and use network-layer anonymity layers such as Tor \cite{tor} alongside their existing Bitcoin clients when introducing new transactions into the network. Such requirements make such variations less appealing from a usability perspective. Furthermore, since low-latency anonymity layers like Tor are susceptible to strategic timing attacks by adaptive global adversaries, and transactions do not have real-time constraints in which they must be broadcasted throughout the network, mixnets are a more appropriate solution for achieving sender anonymity. To this end, we introduce Bitcoin Boomerang, a distribtued, collaborative, application-level protocol for achieving mixnet-like behavior to increase sender anonymity. Boomerang is intended to run at the application-layer \emph{within} Bitcoin software clients as an extension of the Bitcoin protocol. We analyze the anonymity properties of Boomerang, and assess the induced performance overhead using a custom simulator that emulates the behavior of Bitcoin nodes (software clients) adhering to the protocol. Our preliminary results indicate that with appropriate parameter tuning, increased sender anonymity with a single software client can be achieved for the small price of increased computational overhead and network bandwidth consumption for each participating Bitcoin user.
\end{abstract}

\IEEEpeerreviewmaketitle

\input{01-introduction}
\input{02-overview}
\input{04-design}
\input{03-properties}
\input{05-performance}
\input{06-related}

\begin{thebibliography}{1}

\bibitem{bitcoin} Satoshi Nakamoto. Bitcoin: A Peer-to-Peer Electronic Cash System. \emph{Consulted} 1 (2008).

\bibitem{Chaum81-Mix} David L. Chaum. Untraceable electronic mail, return addresses, and digital pseudonyms. \emph{Communications of the ACM} 24(2) (1981), 84-90.

\bibitem{tarzan} Michael J. Freedman and Robert Morris. Tarzan: A Peer-to-Peer Anonymizing Network Layer. In \emph{Proceedings of the 9th ACM conference on Computer and Communications Security}, ACM (2002).

\bibitem{AnonymityTerms} A. Pfitzmann AND M. K\o{o}hntopp. Anonymity, Unobservability and Pseudonymity — A Proposal for Terminology. \emph{In Federrath} 12, 1-9.

\bibitem{kaminsky} Dan Kaminsky. Black Ops of TCP/IP Presentation. \emph{Black Hat, Chaos Communication Camp} (2011).

\bibitem{chaumain} David L. Chaum. Blind Signatures for Untraceable Payments. \emph{Crypto} 82 (1982).

\bibitem{zerocoin} Ian Miers, Christina Garman, Matthew Green, Aviel D. Rubin. Zerocoin: Anonymous Distributed E-Cash from Bitcoin. \emph{IEEE Symposium on Security and Privacy} (2013).

\bibitem{bitcoin-tor-wiki} Tor. Bitcoin Wiki. Available online at \url{https://en.bitcoin.it/wiki/Tor}. Last accessed: 1/25/14.

\bibitem{nist-prng} Elaine Barker and John Kelsey. Recommendation for Random Number Generation Using Deterministic Random Bit Generators. 2012. Available online at: \url{http://csrc.nist.gov/publications/nistpubs/800-90A/SP800-90A.pdf}. Last accessed: 2/10/14. 

\bibitem{tor} Roger Dingledine, Nick Mathewson, and Paul Syverson. Tor: The Second-Generation Onion Router. \emph{Naval Research Lab Washington DC} (2004).

\bibitem{jyaml} JYaml - Yaml library for the Java language. Available online at \url{http://jyaml.sourceforge.net/}. Last accessed: 2/10/14. 

% \bibitem{Androulaki12-privacy} Elli Androulaki, Ghassan O. Karame, Marc Roeschlin, Tobias Scherer, and Srdjan Capkun. Evaluating User Privacy in Bitcoin. \emph{IACR Cryptology ePrint Archive} 596 (2012).

% \bibitem{Shamir13-bitcoingraph} Dorit Ron and Adi Shamir. Quantitative Analysis of the Full Bitcoin Transaction Graph. \emph{IACR Cryptology ePrint Archive} 584 (2012).

% \bibitem{ReidHarrigan13} Fergal Reid and Martin Harrigan. An Analysis of Anonymity in the Bitcoin System. \emph{Security and Privacy in Social Networks}, Springer New York (2013), 197-223.

\bibitem{BetterToBitter} Simon Barber, Xavier Boyen, Elaine Shi, and Ersin Uzun. Bitter to Better -- How to Make Bitcoin a Better Currency. \emph{Financial Cryptography and Data Security}, Springer Berlin Heidelberg (2012), 399-414.

% \bibitem{Fistful12} Sarah Meiklejohn, Marjori Pomarole, Grant Jordan, Kirill Levchenko, Damon McCoyy, Geoffrey M. Voelker, and  Stefan Savage. A Fistful of Bitcoins: Characterizing Payments Among Men with No Names. In \emph{Proceedings of the 2013 Conference on Internet Measurement Conference}, ACM (2013).

% \bibitem{coinjoin} G. Maxwell. Coinjoin: Bitcoin Privacy for the Real World. Available online at \url{https://bitcointalk.
% org/index.php?topic=279249.0}. Last accessed: 1/31/14.

\bibitem{pinocchio} George Danezis, C\'{e}dric Fournet, Markulf Kohlweiss, Bryan Parno. Pinocchio Coin: Building Zerocoin from a Succinct Pairing-Based Proof System. In \emph{Proceedings of the First ACM Workshop on Language Support for Privacy-Enhancing Technologies}, ACM (2013).

\bibitem{mixcoin} Joseph Bonneau, Arvind Narayan, Andrew Miller, Jeremy Clark, and Joshua A. Kroll. Mixcoin - Anonymity for Bitcoin with accountable mixes. Preprint available online at: \url{http://cs.umd.edu/~amiller/mix.pdf}.

\bibitem{nist-curves} Darrel Hankerson and Alfred Menezes. NIST Elliptic Curves. \emph{Encyclopedia of Cryptography and Security} (2011), 843-844.

% \bibitem{nist-beacon} NIST Randomness Beacon. Available online at: \url{http://www.nist.gov/itl/csd/ct/nist_beacon.cfm}. Last accessed: 2/5/14.

\end{thebibliography}

\appendix 
\addcontentsline{toc}{chapter}{APPENDICES}

\section{Extended Simulation Results}
Table \ref{tab:extended-results} contains an extended set of experimental results acquired from our simulator. Observe that in all cases the average message latency, measured in discrete time epochs, is quite reasonable since a single epoch is approximately equal to 0.1s. For example, a message latency of 9918.31 epochs is approximately equivalent to 992s, which is roughly 16 minutes. Since there are no real-time constraints on transaction broadcast introduction, and double-spending is prevented by miners who verify the first instance of a broadcasted transaction, we believe such a delay is reasonable.
\begin{table*}
\begin{center}
\caption{Extended simulation results including average message latency and traffic generation rates ($\pi$ and $\sigma$).}
\label{tab:extended-results}
    \begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
    $n$ & $\pi$ & $\sigma$ & {\bf Avg. Latency} & {\bf Avg. Chaff Generated} & {\bf Avg. Transactions Encoded} & {\bf Avg. Forwarded Messages} & {\bf Avg. Retries} \\ \hline
  % N, pi, sigma, avgLatency, avgChaffComputations, avgTxComputtions, avgForwarded, avgRetries
2000 & 200 & 1000 & 9918.31 & 343.35 & 7.78 & 180.79 & 0.96 \\
2000 & 200 & 1000 & 2780.40 & 488.42 & 15.91 & 179.17 & 0.00 \\
2000 & 200 & 1000 & 3577.19 & 1082.87 & 31.84 & 415.03 & 0.00 \\
2000 & 200 & 1000 & 10218.64 & 4528.39 & 96.28 & 2758.08 & 0.75 \\
2000 & 200 & 1000 & 18528.48 & 16059.35 & 273.23 & 5814.22 & 1.88 \\
2000 & 200 & 1000 & 9121.64 & 324.26 & 7.97 & 159.93 & 0.99 \\
2000 & 2000 & 5000 & 3296.00 & 148.19 & 42.54 & 29.80 & 0.00 \\
2000 & 2000 & 5000 & 46249.89 & 6916.45 & 1053.30 & 3483.64 & 6.34 \\
2000 & 2000 & 5000 & 3972.31 & 198.35 & 47.36 & 66.26 & 0.00 \\
2000 & 2000 & 5000 & 32704.14 & 3603.02 & 568.94 & 2599.06 & 5.01 \\
2000 & 2000 & 5000 & 3970.25 & 197.43 & 47.36 & 66.19 & 0.00 \\
2000 & 2000 & 5000 & 33929.58 & 3890.12 & 605.98 & 2673.71 & 5.40 \\
2000 & 2000 & 5000 & 56236.27 & 11361.13 & 1692.57 & 6402.18 & 10.93 \\
2000 & 2000 & 5000 & 3830.50 & 178.52 & 47.38 & 52.89 & 0.00 \\
200 & 200 & 1000 & 15411.71 & 3592.23 & 66.20 & 3030.34 & 15.49 \\
200 & 200 & 1000 & 35780.14 & 6052.75 & 97.88 & 3784.15 & 11.45 \\
200 & 200 & 1000 & 49408.82 & 5255.79 & 80.54 & 2464.30 & 5.83 \\
200 & 200 & 1000 & 15041.98 & 4424.46 & 87.00 & 3797.90 & 4.09 \\
200 & 200 & 1000 & 34192.21 & 11456.77 & 198.34 & 6859.86 & 5.28 \\
200 & 200 & 1000 & 44278.54 & 18685.20 & 285.63 & 7797.51 & 5.05 \\
200 & 200 & 1000 & 10695.88 & 3319.69 & 67.26 & 2208.28 & 0.79 \\
200 & 200 & 1000 & 31071.47 & 19921.87 & 348.41 & 11336.27 & 4.51 \\
200 & 200 & 1000 & 15859.56 & 29871.07 & 567.61 & 25852.14 & 8.74 \\
200 & 200 & 1000 & 35890.42 & 101208.49 & 1591.11 & 60676.89 & 15.83 \\
200 & 2000 & 5000 & 22007.83 & 95.52 & 17.23 & 79.04 & 4.07 \\
200 & 2000 & 5000 & 46316.93 & 218.59 & 33.93 & 123.64 & 4.01 \\
200 & 2000 & 5000 & 70855.82 & 337.74 & 50.17 & 156.51 & 3.87 \\
200 & 2000 & 5000 & 16385.33 & 371.22 & 67.33 & 347.38 & 3.58 \\
200 & 2000 & 5000 & 35475.20 & 814.33 & 128.44 & 570.80 & 3.66 \\
200 & 2000 & 5000 & 58155.07 & 1363.12 & 201.09 & 647.35 & 3.91 \\
200 & 2000 & 5000 & 16249.05 & 760.73 & 135.37 & 643.99 & 3.63 \\
200 & 2000 & 5000 & 36339.58 & 1841.39 & 286.72 & 1150.79 & 4.28 \\
200 & 2000 & 5000 & 59842.71 & 2883.20 & 427.02 & 1265.85 & 4.24 \\
200 & 2000 & 5000 & 15539.04 & 1162.00 & 202.93 & 1004.22 & 3.33 \\
200 & 2000 & 5000 & 36597.48 & 2641.06 & 411.73 & 1548.01 & 4.09 \\
200 & 2000 & 5000 & 56703.05 & 4307.92 & 635.29 & 1905.60 & 4.21 \\
200 & 2000 & 5000 & 32079.91 & 37.29 & 6.80 & 16.56 & 1.50 \\
200 & 2000 & 5000 & 43757.67 & 81.37 & 12.95 & 16.95 & 1.42 \\
200 & 2000 & 5000 & 16949.92 & 152.76 & 27.91 & 89.56 & 1.51 \\
200 & 2000 & 5000 & 34974.36 & 448.44 & 71.17 & 135.03 & 1.91 \\
200 & 2000 & 5000 & 62589.00 & 792.99 & 120.90 & 163.91 & 2.15 \\
200 & 2000 & 5000 & 15324.64 & 392.49 & 71.88 & 251.08 & 1.78 \\
200 & 2000 & 5000 & 34836.53 & 834.26 & 133.21 & 268.63 & 1.79 \\
200 & 2000 & 5000 & 56656.67 & 1268.65 & 193.09 & 259.45 & 1.73 \\
200 & 2000 & 5000 & 15666.90 & 510.83 & 93.52 & 318.95 & 1.55 \\
200 & 2000 & 5000 & 31933.98 & 957.48 & 151.80 & 271.72 & 1.39 \\
200 & 2000 & 5000 & 53678.33 & 1613.27 & 243.98 & 324.57 & 1.49 \\ \hline
    \end{tabular}
  \end{center}
\end{table*}


% that's all folks
\end{document}


